The analogue method for precipitation prediction: finding better analogue situations at a sub-daily time step

### 2017-03-24 Moving temporal window - HESS/template.tex
HESS paper under work.

%TODO: change CRPSS from % to 0.x ?

@@

	Section \ref{sec:data_methods} presents the context of the study as well as the data and methods, including the proposed MTW technique. The impact of the reduction of the archive and the improvements brought by the MTW are assessed in Sect. \ref{sec:results}. The benefits of introducing a MTW were assessed first in regards to the analogy criterion improvement between synoptic situations (Sect. \ref{sec:influence_criteria}) and then in terms of precipitation prediction skill (Sect. \ref{sec:influence_scores}). Finally, the results are discussed in Sect. \ref{sec:discussion}, and the conclusions are found in Sect. \ref{sec:conclusions}.

@@

	Synoptic-scale variables, used as predictors, were extracted from two of the most recent global reanalysis datasets: the european ERA-20C \citep{Poli2016} with a 3h temporal resolution, and a spatial resolution of 1\textdegree, and MERRA-2, from NASA, with a 6h temporal resolution and a spatial resolution of 0.625\textdegree x 0.5\textdegree. The study was originally performed on the NCEP/NCAR reanalysis 1 dataset \citep{Kalnay1996}, and the conclusions were similar. ERA-20C is build by assimilating only surface observations, and is thus available on a long period (1900\textendash 2010). On the contrary, MERRA-2 is build by assimilating observations at higher levels and from more sensors, including satellite data, but is then more limited in time (1980\textendash present). It is of interest to consider these two datasets, as they represent different kind of products and are thus an interesting basis to assess the relevance of a MTW. The specific advantages of ERA-20C is that it allows testing the relevance of the MTW at a 3h time step, and covers a long period. On the other hand, MERRA-2 has a higher spatial resolution and can be expected to be more correct at higher levels of the atmosphere.

@@

@@

	\begin{enumerate}
		\item Manual selection of the following parameters:
		\begin{enumerate}
			\item meteorological variable (e.g. geopotential height, temperature, relative humidity, etc.),
			\item pressure level (e.g. 500 hPa, ...),
			\item temporal window (hour of the day \textendash\ e.g. 6:00 or 12:00~UTC),
			\item initial analogue numbers (e.g. $N_{1}=50$).
		\end{enumerate}

		\item For every level of analogy:
		\begin{enumerate}
			\item Identification of the most skilled unitary cell (one point for moisture variables and four for geopotential heights when using the S1 criterion) over a large domain. Every point (or cell) of the full domain is assessed on all predictors of the level of analogy, jointly (consisting generally of the same variable but on different pressure levels and at different hours).
			\item From this most skilled point, the spatial window is expanded by successive iterations in the direction of greater performance gain. The spatial window grows by repeating the previous steps until no improvement is reached.
			\item The number of analogue situations $N_{1}$ is then reconsidered and optimized for the current level of analogy.
		\end{enumerate}
		\item A new level of analogy can then be added, based on other variables (such as the moisture index) at chosen pressure levels and hours of the day. The number of analogues for the next level of analogy, $N_{2}$, is initiated at a chosen value. The procedure starts again from step 2 (calibration of the spatial window and the number of analogues) for the new level. The parameters calibrated on the previous analogy levels are fixed and do not change. 
		\item Finally, the numbers of analogues $N_{1}$ and $N_{2}$ for the different levels of analogy are reassessed. This is done iteratively by varying the number of analogues of each level in a systematic way.
	\end{enumerate}

	The calibration is done in successive steps with a limited number of parameters. Previously calibrated parameters are generally not reassessed (except for the number of analogues). More advanced techniques, such as using genetic algorithms \citep{Horton2016}, exist but are out of the scope of the present study.

	\subsection{Performance score}
	\label{sec:performance}

	In order to assess the performance of AMs, the continuous ranked probability score \citep[CRPS,][]{Brown1974, Matheson1976, Hersbach2000} is often employed \citep[see, e.g.,][]{Bontron2004, Bontron2005, BenDaoud2008, Horton2012, Marty2012, Radanovics2013, Chardon2014, Junk2015, BenDaoud2016, Caillouet2016}. It allows the evaluation of the predicted cumulative distribution functions $F(y)$ of the precipitation values $y$ from analogue situations compared to the observed value $y^{0}$. A better prediction has a smaller score. It is defined as follows:

@@

	In order to compare the value of the score in regard to a reference, one often considers its skill score expression and uses the climatological distribution (i.e., the distribution of all precipitation values from the corresponding archive) as the reference. The continuous ranked probability skill score (CRPSS) is defined as follows:

	\begin{equation}
	\label{eq:CRPSS}
	S_{\text{SCRP}} = \frac{S_{\text{CRP}}-S_{\text{CRP}}^{r}}{S_{\text{CRP}}^{p}-S_{\text{CRP}}^{r}} = 1-\frac{S_{\text{CRP}}}{S_{\text{CRP}}^{r}}
	\end{equation}
	where $S_{\text{CRP}}^{r}$ is the $S_{\text{CRP}}$ value for the reference (climatological distribution) and $S_{\text{CRP}}^{p}$ is for a perfect prediction (which implies $S_{\text{CRP}}^{p}~=~0$). A better prediction is characterized by an increase in CRPSS: $S_{\text{SCRP}}~=~1$ for a perfect prediction and $S_{\text{SCRP}}~<~0$ for a prediction with a lower skill than the reference.

@@

	The moving time window (MTW) technique aims at finding better analogue situations at different hours of the day rather than comparing the predictors at the same fixed hours. If the target situation is kept at 12:00 and 24:00~UTC for Z1000 and Z500 respectively, candidate situations are not only considered at 12:00 and 24:00~UTC, but at other hours by allowing a time shift. Therefore, instead of looking for analogues at a 24h time step, they are sought at the time step matching the predictor temporal resolution which is a 6h time step in this study (Fig. \ref{fig:principle}).

	The target situations and their corresponding observed precipitation values do not change because the prediction is still established on a daily basis for a fixed period of the target day (6:00~UTC to 6:00~UTC the next day) as before. The difference is that the candidates are 4 times as many (even though they are not fully independent) as in the conventional approach. No constraint was added in order to restrict the selection of multiple analogues within the same candidate dates.

	In order to assess the benefit of searching for analogue situations at a sub-daily time step for quantitative precipitation prediction, an appropriate precipitation series is required. On the basis of high temporal resolution time series (Sect. \ref{sec:data}), 24h totals were processed at a 6h time step by means of a moving 24h total. Since sub-daily precipitation time series are available on a shorter period than daily ones, the loss of performance resulting from a reduction of a 47~year archive (1961\textendash 2008) to 25~years (1982\textendash 2007) can be expected. However, the competition between the loss of performance due to a smaller archive length and the potentially better analogy between target and MTW candidates needs to be assessed.

@@

	\subsection{Influence of the MTW on the analogy criterion}
	\label{sec:influence_criteria}

@@

	The new performance scores (CRPSS) of the precipitation prediction are provided in Fig. \ref{fig:plots_CRPSS_2Z} and \ref{fig:plots_CRPSS_2Z-2MI} for the 2Z and 2Z-2MI methods, respectively, for the reduced archive (1982\textendash 2007). The gains relative to the static approach on the same archive ranged from 0.57 to 2.14 points (\% of CRPSS) for the 2Z method and from 1.53 to 2.20 points for the 2Z-2MI method.

	\subsubsection{Improvement per precipitation classes}
	\label{sec:improvement_CRPSS_precip_threshold}

@@

	The values of the CRPSS scores for both methods (Fig. \ref{fig:plots_CRPSS_2Z} and \ref{fig:plots_CRPSS_2Z-2MI}) have significantly increased after recalibration. When analysing the change in performance per precipitation class, the results (not shown) were very similar to the observations in Sect. \ref{sec:improvement_CRPSS_precip_threshold}, with a slight performance increase for small precipitation values that can be observed at the expense of higher amounts, due to the higher number of analogues.

	\subsection{Using a reconstructed archive}
	\label{sec:reconstruction_results}

	When using the first reconstructed time series based on the proportional distribution (see Sect. \ref{sec:reconstruction}), the AM performance was degraded and was even below the conventional method without MTW (Table \ref{table:disaggregation_proportional} to compare to Fig. \ref{fig:plots_CRPSS_2Z} and \ref{fig:plots_CRPSS_2Z-2MI}).

	For the second approach, the synoptic proxy for the temporal disaggregation of the daily time series had to be identified first. The results are illustrated this time for the Zermatt station. Among the considered moisture variables (see Sect. \ref{sec:reconstruction}), the best proxy was the precipitable water at 45\textdegree\ N and 7.5\textdegree\ E, with a time offset of \textendash 6~h (Table \ref{table:proxy_correlations}). Table \ref{table:proxy_CRPSS} presents the CRPSS scores obtained by the disaggregated series using the proxy of precipitable water which are also lower than the conventional method.

@@

@@

	The impact of the archive reduction can be seen in Fig. \ref{fig:plots_CRPSS_2Z} for the 2Z method and in Fig. \ref{fig:plots_CRPSS_2Z-2MI} for the 2Z-2MI method. As expected, a loss of performance was observed for each station, except for that of Aigle, which seemed relatively indifferent to this change. This loss was globally significant, with up to \textendash 1.89 points (\% of CRPSS) for Visp and the 2Z method.

	\subsection{Improvement of the selection of analogue situations}

	\subsection{Improvement of precipitation prediction}

	The MTW was found to improve the skill of the precipitation prediction for both the 2Z and 2Z-2MI methods (Fig. \ref{fig:plots_CRPSS_2Z} and \ref{fig:plots_CRPSS_2Z-2MI}, Sect. \ref{sec:influence_scores}). Moreover, it required no additional predictor. With the introduction of the MTW, the performance loss related to the reduction of the archive length was negated (considering a 25 year archive of sub-daily data; the difference could be higher with a shorter archive). It was in this case of the same magnitude as if the length of the archive doubled. Note, that despite the number of candidate situations being 4 times as many, the gains seem to be lower than for a quadrupled archive length. The likely reason is that an actual longer archive would contain more atmospheric situations that might have been observed less frequently during a shorter period. Moreover, high correlations between sub-daily circulation patterns are expected. The MTW, therefore, did not create 4 times as many independent data, but the increase in information was nevertheless substantial. In this regards, a reanalysis dataset with a higher temporal resolution might not improve the performance significantly more than a 6-hourly dataset. In contrast, reducing the MTW to a 12-hour time step might reduce redundancy in the archive, but might also reduce the chance of finding better analogue situations, as circulation patterns can evolve substantially in 12~hours.

	Both the analogy criteria (Sect. \ref{sec:influence_precip}) and the performance scores (Sect. \ref{sec:improvement_CRPSS_precip_threshold}) were improved to a greater extent for days with heavier precipitation. This is likely due to the fact that higher precipitation events are a consequence of atmospheric conditions with greater dynamics, such as weather disturbances, which have a well-marked temporal evolution. Indeed, the position of the driving elements, such as the low pressure centres and the fronts, change significantly during a day. These situations are less numerous than anticyclonic situations, which makes it less likely to find very good analogues at the same time of the day. We can, therefore, expect to improve these situations with greater dynamics more significantly when introducing a MTW, as better matches to the target situation may be found. In contrast, days with low dynamics in the atmospheric circulation, such as anticyclonic situations, will not be radically improved by the introduction of the MTW.

	\subsection{Seasonal effect}

@@

	\subsection{On the use of an old reanalysis dataset}
	\label{sec:old_reanalysis}

	The considered reanalysis dataset, which is the NCEP/NCAR reanalysis 1 \citep{Kalnay1996}, is relatively old and has a coarse resolution (2.5\textdegree). Newer reanalysis datasets could have been used in this study and might have resulted in higher performance scores. However, \cite{BenDaoud2009} showed that the sensitivity of the method to the reanalysis dataset is rather small. This is particularly true for simple AMs that mainly rely on the atmospheric circulation, which is already well defined at a coarser resolution. That might not be the case in more elaborate methods relying on thermodynamic data. A comparative analysis of several reanalysis datasets within the AM is being conducted and will be the topic of a dedicated study.

	Moreover, one can assume that the gain observed here by introducing a MTW should also be found for a better reanalysis dataset. Indeed, a better dataset does not negatively influence the fact that one can find better analogue situations at other hours of the day rather than at fixed hours.

@@

@@

	\begin{labeling}{2Z-2MI}
		\item [2Z] Name of the analogue method of the atmospheric circulation
		\item [2Z-2MI] Name of the analogue method composed of a first level on the atmospheric circulation and a second level on a moisture index
		\item [AM] Analogue method
		\item [CRPS] Continuous ranked probability score
		\item [CRPSS] Continuous ranked probability skill score
		\item [MTW] Moving time window
		\item [NCAR] National Center for Atmospheric Research
		\item [NCEP] National Center for Environmental Prediction
		\item [RH850] Relative humidity at 850 hPa
		\item [RMSE] Root-mean-square error
		\item [S1] Teweles and Wobus (1954) score
		\item [TPW] Total precipitable water
		\item [Z1000] Geopotential height at 1000 hPa
		\item [Z500] Geopotential height at 500 hPa
	\end{labeling}

@@

	\begin{figure}[htb]
		\includegraphics[width=8.3cm]{fig03.pdf}
		\caption{Performance score (CRPSS) of the AM on the atmospheric circulation at the different stations for (dashed) the full archive, i.e. 1961\textendash 2008; (yellow) the reduced archive, i.e. 1982\textendash 2007; (blue) the introduction of the MTW on the reduced archive; and (green) the recalibrated parameters of the AM with the MTW.}
		\label{fig:plots_CRPSS_2Z}
	\end{figure}

	\begin{figure}[htb]
		\includegraphics[width=8.3cm]{fig04.pdf}
		\caption{Same as Figure \ref{fig:plots_CRPSS_2Z}, but for the analogue method with a second level with the moisture variables.}
		\label{fig:plots_CRPSS_2Z-2MI}
	\end{figure}

@@

	\begin{figure}[htb]
		\includegraphics[width=8.3cm]{fig10.pdf}
		\caption{Differences of the CRPSS performance score due to the introduction of the MTW as a function of daily precipitation thresholds at the Ulrichen station. The stars represent averages.}
		\label{fig:changes_CRPS_precip_threshold}
	\end{figure}

@@

	\begin{table}[htb]
		\caption{Values of the CRPSS (\%) score for the original and the recalibrated parameters (with the sequential method, as described in Sect. \ref{sec:calibration}) using the MTW approach on the disaggregated precipitation time series (short period) by means of the proportional distribution.}
		\begin{center}
			\begin{tabular}{l c c c c}
				\hline
				\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{ 2}{c}{2Z-2MI} \\
				& original & recalib. & original & recalib. \\
				\hline
				Ulrichen & 29.13 & 29.61 & 33.15 & 33.45 \\
				Zermatt & 22.17 & 22.80 & 26.72 & 27.43 \\
				Visp & 22.32 & 22.89 & 27.01 & 28.04 \\
				Montana & 29.41 & 30.24 & 33.83 & 34.55 \\
				Sion & 22.98 & 23.41 & 28.57 & 29.15 \\
				Aigle & 29.07 & 29.46 & 34.66 & 35.09 \\
				\hline
			\end{tabular}
		\end{center}
		\label{table:disaggregation_proportional}
	\end{table}

	\begin{table}[htb]
		\caption{Value of the coefficient of determination between the reconstructed 6-hourly precipitation time series using the listed variables and the accurate time series for the period 1982\textendash 2007. The grid points surrounding the region are: 1) 5\textdegree\ E, 47.5\textdegree\ N; 2) 5\textdegree\ E, 45\textdegree\ N; 3) 7.5\textdegree\ E, 47.5\textdegree\ N; and 4) 7.5\textdegree\ E, 45\textdegree\ N. The highest coefficient of determination is indicated in bold.}
		\begin{center}
			\begin{tabular}{l c c c c c c}
				\hline
				\multirow{2}{*}{Variable} & \multirow{2}{*}{Point} &  \multicolumn{5}{c}{Time lapse} \\
				&  & \textendash 12 h & \textendash 6 h & 0 h & +6 h & +12 h \\ 
				\hline
				\multirow{ 4}{*}{RH1000} & 1 & 0.668 & 0.669 & 0.684 & 0.683 & 0.670 \\
				& 2 & 0.669 & 0.669 & 0.683 & 0.681 & 0.669 \\
				& 3 & 0.662 & 0.673 & 0.691 & 0.682 & 0.673 \\
				& 4 & 0.666 & 0.671 & 0.688 & 0.681 & 0.668 \\ \hline
				\multirow{ 4}{*}{RH925} & 1 & 0.672 & 0.673 & 0.684 & 0.684 & 0.675 \\
				& 2 & 0.674 & 0.674 & 0.683 & 0.682 & 0.672 \\
				& 3 & 0.662 & 0.673 & 0.691 & 0.682 & 0.673 \\
				& 4 & 0.666 & 0.671 & 0.689 & 0.681 & 0.668 \\ \hline
				\multirow{ 4}{*}{RH850} & 1 & 0.675 & 0.675 & 0.679 & 0.678 & 0.671 \\
				& 2 & 0.681 & 0.690 & 0.691 & 0.677 & 0.664 \\
				& 3 & 0.665 & 0.680 & 0.693 & 0.683 & 0.675 \\
				& 4 & 0.675 & 0.694 & 0.706 & 0.681 & 0.659 \\ \hline
				\multirow{ 4}{*}{TCW} & 1 & 0.688 & 0.687 & 0.667 & 0.655 & 0.652 \\
				& 2 & 0.697 & 0.699 & 0.669 & 0.644 & 0.644 \\
				& 3 & 0.686 & 0.708 & 0.689 & 0.655 & 0.648 \\
				& 4 & 0.696 & \textbf{0.721} & 0.696 & 0.643 & 0.636 \\ \hline
			\end{tabular}
		\end{center}
		\label{table:proxy_correlations}
	\end{table}

	\begin{table}[htb]
		\caption{Values of the CRPSS (\%) score for Zermatt for the original and the recalibrated parameters (with the sequential method, as described in Sect. \ref{sec:introduction}) using the MTW approach on the disaggregated precipitation time series (short and long periods) by means of proxy variables from the reanalysis dataset.}
		\begin{center}
			\begin{tabular}{l c c c c}
				\hline
				\multirow{2}{*}{Period} & \multicolumn{2}{c}{2Z} & \multicolumn{ 2}{c}{2Z-2MI} \\
				& original & recalib. & original & recalib. \\
				\hline
				1982\textendash 2007 & 22.57 & 23.14 & 27.11 & 27.71 \\
				1961\textendash 2008 & 23.81 & 24.38 & 28.42 & 28.86 \\
				\hline
			\end{tabular}
		\end{center}
		\label{table:proxy_CRPSS}
	\end{table}

>>>>

@@

	Section \ref{sec:data_methods} presents the context of the study as well as the data and methods, including the proposed MTW technique. The impact of the reduction of the archive and the improvements brought by the MTW are assessed in Sect. \ref{sec:results}. The benefits of introducing a MTW were assessed first in regards to the analogy criterion improvement between synoptic situations (Sect. \ref{sec:influence_analogue_dates}) and then in terms of precipitation prediction skill (Sect. \ref{sec:influence_scores}). Finally, the results are discussed in Sect. \ref{sec:discussion}, and the conclusions are found in Sect. \ref{sec:conclusions}.

@@

	Synoptic-scale variables, used as predictors, were extracted from two of the most recent global reanalysis datasets: the european ERA-20C \citep{Poli2016} with a 3h temporal resolution, and a spatial resolution of 1\textdegree, and MERRA-2, from NASA, with a 6h temporal resolution and a spatial resolution of 0.625\textdegree x 0.5\textdegree. The study was originally performed on the NCEP/NCAR reanalysis 1 dataset \citep{Kalnay1996}, and the conclusions were similar. ERA-20C is build by assimilating only surface observations, and is thus available on a long period (1900\textendash 2010). On the contrary, MERRA-2 is build by assimilating observations at higher levels and from more sensors, including satellite data, but is then more limited in time (1980\textendash present). It is of interest to assess the relevance of a MTW with these two datasets, as they represent different kind of products. The specific advantages of ERA-20C is that it allows testing a MTW with a 3h time step, and it covers a long period. On the other hand, MERRA-2 has a higher spatial resolution and can be expected to be more correct at higher levels of the atmosphere.

@@

	AMs rely on parameters that need to be defined for every level of analogy. Here, the selection of the meteorological variables used as predictors, as well as their corresponding analogy criteria, pressure level, and hour of the day will be identical to the methods 2Z (Table \ref{table:method_2Z}) and 2Z-2MI (Table \ref{table:method_2Z-2MI}) described above. The parameters that are here calibrated are:

	\begin{itemize}
		\item The spatial windows, which are the domains on which predictors are compared. There is a spatial window specific to each level of analogy. It will thus differ between circulation and moisture variables.
		\item The optimal number of analog situations for every level of analogy.
	\end{itemize}

@@

	\begin{enumerate}
		\item For every level of analogy:
		\begin{enumerate}
			\item Identification of the most skilled unitary cell (one point for moisture variables and four for geopotential heights when using the S1 criterion) over a large domain. Every point (or cell) of the full domain is assessed on all predictors of the level of analogy, jointly (consisting generally of the same variable but on different pressure levels and at different hours).
			\item From this most skilled point, the spatial window is expanded by successive iterations in the direction of greater performance gain. The spatial window grows by repeating the previous steps until no improvement is reached.
			\item The number of analogue situations $N_{1}$, which was initially set at an arbitrary value, is then reconsidered and optimized for the current level of analogy.
		\end{enumerate}
		\item A new level of analogy can then be added, based on other variables (such as the moisture index) at chosen pressure levels and hours of the day. The number of analogues for the next level of analogy, $N_{2}$, is initiated at a chosen value. The procedure starts again from step 1 (calibration of the spatial window and the number of analogues) for the new level. The parameters calibrated on the previous analogy levels are fixed and do not change. 
		\item Finally, the numbers of analogues $N_{1}$ and $N_{2}$ for the different levels of analogy are reassessed. This is done iteratively by varying the number of analogues of each level in a systematic way.
	\end{enumerate}

	The calibration is done in successive steps with a limited number of parameters in order to minimize the objective function (CRPS, Eq. \ref{eq:CRPS}). Previously calibrated parameters are generally not reassessed (except for the number of analogues). More advanced techniques, such as using genetic algorithms \citep{Horton2017}, exist but are out of the scope of the present study.

	The 29-yr hourly precipitation dataset was divided into a calibration period (CP) and a validation period (VP), in order to assess the robustness of the proposed improvements on independent data. The selection of the VP was evenly distributed over the entire series \citep{BenDaoud2010} to reduce potential biases related to trends linked to climate change or to the evolution in measurement techniques. Thus, one out of every five years was selected for validation, which represents a total of 6 years for the VP and 23 for the CP.

	The continuous ranked probability score \citep[CRPS,][]{Brown1974, Matheson1976, Hersbach2000} is often employed in order to assess the performance of AMs \citep[see, e.g.,][]{Bontron2004, Bontron2005, BenDaoud2008, Horton2012, Marty2012, Radanovics2013, Chardon2014, Junk2015, BenDaoud2016, Caillouet2016}. It allows the evaluation of the predicted cumulative distribution functions $F(y)$ of the precipitation values $y$ from analogue situations compared to the observed value $y^{0}$. A better prediction has a smaller score. It is defined as follows:

@@

@@

	The moving time window (MTW) technique aims at finding better analogue situations at different hours of the day rather than comparing the predictors at the same fixed hours. If the target situation is kept at 12:00 and 24:00~UTC for Z1000 and Z500 respectively, candidate situations are not only considered at 12:00 and 24:00~UTC, but at other hours by allowing a time shift. Therefore, instead of looking for analogues at a 24h time step, they are sought at the time step matching the predictor temporal resolution. The ERA-20C dataset made here possible to test a MTW with a 12h, 6h, or 3h time step (named respectively 12h-MTW, 6h-MTW, 3h-MTW hereafter; Fig. \ref{fig:principle}).

	The target situations and their corresponding observed precipitation values do not change because the prediction is still established on a daily basis for a fixed period of the target day (6:00~UTC to 6:00~UTC the next day) as before. The difference is that the candidates are 2 (12h-MTW), 4 (6h-MTW), or 8 (3h-MTW) times as many (even though they are not fully independent) as in the conventional approach. No constraint was added in order to restrict the selection of multiple analogues within the same candidate dates.

	In order to assess the benefit of searching for analogue situations at a sub-daily time step for quantitative precipitation prediction, an appropriate precipitation series is required. On the basis of high temporal resolution time series (Sect. \ref{sec:data}), 24h totals were processed at time steps matching the MTW by means of a moving 24h total on the period 1982-2010.

@@

	The AMs were applied to both ERA-20C and MERRA-2 datasets. Most results are presented for the ERA-20C dataset, as it allows testing a 3h-MTW, but would lead to similar conclusions with MERRA-2. The impact of an MTW was assessed on two different basis:
	\begin{itemize}
		\item Original parameters: The AMs were initially calibrated for each station based on the classic 24-hr approach. Then, the MTW was introduced into the AMs, but the parameters (spatial windows and number of analogues) were not reassessed. The analogy is the same and thus initial analogue dates should be found in the new distribution, along with new dates provided by the MTW.
		\item Recalibrated: The parameters of the AMs were reassessed after the introduction of the MTW at different time steps. This allowed to improve the prediction skill of the AMs by adapting to the new information available through the MTW. The characterization of the analogy might thus change (different spatial windows and number of analogues).
	\end{itemize}

	The MTW is expected to have an impact on both the selection of analogue dates and the prediction skill. Both will be analyzed separately hereafter.

	\subsection{Influence of the MTW on the selection of analogue dates}
	\label{sec:influence_analogue_dates}

	\subsubsection{Changes in the analogy criteria distributions}
	\label{sec:changes_distributions}

@@

	The new performance scores (CRPS) of the precipitation prediction are provided in Fig. \ref{fig:plots_CRPS_2Z} and \ref{fig:plots_CRPS_2Z-2MI} for the 2Z and 2Z-2MI methods, respectively, for the reduced archive (1982\textendash 2007).

	The MTW was found to improve the skill of the precipitation prediction for both the 2Z and 2Z-2MI methods (Fig. \ref{fig:plots_CRPS_2Z} and \ref{fig:plots_CRPS_2Z-2MI}, Sect. \ref{sec:influence_scores}). Moreover, it required no additional predictor. With the introduction of the MTW, the performance loss related to the reduction of the archive length was negated (considering a 25 year archive of sub-daily data; the difference could be higher with a shorter archive). It was in this case of the same magnitude as if the length of the archive doubled. Note, that despite the number of candidate situations being 4 times as many, the gains seem to be lower than for a quadrupled archive length. The likely reason is that an actual longer archive would contain more atmospheric situations that might have been observed less frequently during a shorter period. Moreover, high correlations between sub-daily circulation patterns are expected. The MTW, therefore, did not create 4 times as many independent data, but the increase in information was nevertheless substantial. In this regards, a reanalysis dataset with a higher temporal resolution might not improve the performance significantly more than a 6-hourly dataset. In contrast, reducing the MTW to a 12-hour time step might reduce redundancy in the archive, but might also reduce the chance of finding better analogue situations, as circulation patterns can evolve substantially in 12~hours.

	Both the analogy criteria (Sect. \ref{sec:influence_precip}) and the performance scores (Sect. \ref{sec:improvement_CRPS_precip_threshold}) were improved to a greater extent for days with heavier precipitation. This is likely due to the fact that higher precipitation events are a consequence of atmospheric conditions with greater dynamics, such as weather disturbances, which have a well-marked temporal evolution. Indeed, the position of the driving elements, such as the low pressure centres and the fronts, change significantly during a day. These situations are less numerous than anticyclonic situations, which makes it less likely to find very good analogues at the same time of the day. We can, therefore, expect to improve these situations with greater dynamics more significantly when introducing a MTW, as better matches to the target situation may be found. In contrast, days with low dynamics in the atmospheric circulation, such as anticyclonic situations, will not be radically improved by the introduction of the MTW.

	\subsubsection{Improvement per precipitation classes}
	\label{sec:improvement_CRPS_precip_threshold}

@@

	The values of the CRPS scores for both methods (Fig. \ref{fig:plots_CRPS_2Z} and \ref{fig:plots_CRPS_2Z-2MI}) have significantly increased after recalibration. When analysing the change in performance per precipitation class, the results (not shown) were very similar to the observations in Sect. \ref{sec:improvement_CRPS_precip_threshold}, with a slight performance increase for small precipitation values that can be observed at the expense of higher amounts, due to the higher number of analogues.

@@

	Since sub-daily precipitation time series are available on a shorter period than daily ones, the loss of performance resulting from a reduction of a 47~year archive (1961\textendash 2008) to 25~years (1982\textendash 2007) can be expected. However, the competition between the loss of performance due to a smaller archive length and the potentially better analogy between target and MTW candidates needs to be assessed.

@@

	The impact of the archive reduction can be seen in Fig. \ref{fig:plots_CRPS_2Z} for the 2Z method and in Fig. \ref{fig:plots_CRPS_2Z-2MI} for the 2Z-2MI method. As expected, a loss of performance was observed for each station, except for that of Aigle, which seemed relatively indifferent to this change. This loss was globally significant, with up to \textendash 1.89 points (\% of CRPS) for Visp and the 2Z method.

@@

@@

	When using the first reconstructed time series based on the proportional distribution (see Sect. \ref{sec:reconstruction}), the AM performance was degraded and was even below the conventional method without MTW.

	For the second approach, the synoptic proxy for the temporal disaggregation of the daily time series had to be identified first. The results are illustrated this time for the Zermatt station. Among the considered moisture variables (see Sect. \ref{sec:reconstruction}), the best proxy was the precipitable water at 45\textdegree\ N and 7.5\textdegree\ E, with a time offset of \textendash 6~h. xx presents the CRPS scores obtained by the disaggregated series using the proxy of precipitable water which are also lower than the conventional method.

@@

	\begin{labeling}{2Z-2MI}
		\item [2Z] Name of the analogue method of the atmospheric circulation
		\item [2Z-2MI] Name of the analogue method composed of a first level on the atmospheric circulation and a second level on a moisture index
		\item [AM] Analogue method
		\item [CP] Calibration period
		\item [CRPS] Continuous ranked probability score
		\item [MTW] Moving time window
		\item [NCAR] National Center for Atmospheric Research
		\item [NCEP] National Center for Environmental Prediction
		\item [RH850] Relative humidity at 850 hPa
		\item [RMSE] Root-mean-square error
		\item [S1] Teweles and Wobus (1954) score
		\item [TPW] Total precipitable water
		\item [VP] Validation period
		\item [Z1000] Geopotential height at 1000 hPa
		\item [Z500] Geopotential height at 500 hPa
	\end{labeling}

@@

	\begin{figure}[htb]
		\includegraphics[width=8.3cm]{fig03.pdf}
		\caption{Performance score (CRPS) of the AM on the atmospheric circulation at the different stations for (dashed) the full archive, i.e. 1961\textendash 2008; (yellow) the reduced archive, i.e. 1982\textendash 2007; (blue) the introduction of the MTW on the reduced archive; and (green) the recalibrated parameters of the AM with the MTW.}
		\label{fig:plots_CRPS_2Z}
	\end{figure}

	\begin{figure}[htb]
		\includegraphics[width=8.3cm]{fig04.pdf}
		\caption{Same as Figure \ref{fig:plots_CRPS_2Z}, but for the analogue method with a second level with the moisture variables.}
		\label{fig:plots_CRPS_2Z-2MI}
	\end{figure}

@@

	\begin{figure}[htb]
		\includegraphics[width=8.3cm]{fig10.pdf}
		\caption{Differences of the CRPS performance score due to the introduction of the MTW as a function of daily precipitation thresholds at the Ulrichen station. The stars represent averages.}
		\label{fig:changes_CRPS_precip_threshold}
	\end{figure}

@@
